AHABus \& FCORE: A Modular Bus System for High-Altitude Balloon Missions

### 2017-04-24 chapters/03-methodology.tex
Add reference to NMEA code library

\begin{figure}[H]
\includegraphics[width=0.40\textwidth]{dl-fldigi.png}
\centering
\caption{\acrshort{ahabus} - Ground Segment Software}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=0.40\textwidth]{test-rig.jpg}
\centering
\caption{\acrshort{ahabus} - Test Setup}
\label{fig:exp-setup}
\end{figure}

@@

In order to come as close as possible to real-life conditions, the
\acrshort{gnss} receiver was replaced with an Arduino board programmed to
simulate the position updates of a receiver attached to a \acrlong{hab}
throughout ascent and descent.

>>>>

\begin{figure}[H]
\includegraphics[width=0.80\textwidth]{dl-fldigi.png}
\centering
\caption{\acrshort{ahabus} - Ground Segment Software}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=0.80\textwidth]{test-rig.jpg}
\centering
\caption{\acrshort{ahabus} - Test Setup}
\label{fig:exp-setup}
\end{figure}

@@

In order to come as close as possible to real-life conditions, the
\acrshort{gnss} receiver was replaced with an Arduino board programmed to
simulate the position updates of a receiver attached to a \acrlong{hab}
throughout ascent and descent, using a UKHAS library to emulate NMEA output
(\cite{UKHAS2010}).
